Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-08 longoutput.tex
Add TODO probability analysis
Add reference on checking ground state
Improve reference on Biamonte and Love
Add another reference on checking ground state
Write the ground state check

We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{biamonte_love_2008}.

@@

We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure. The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{kempe_kitaev_regev_2006}.

>>>>

We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.

@@

Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevLett.120.040501} and \cite{PhysRevA.93.022326}.

We write $H$ as a linear combination of tensors of $I$, $X$, and $Z$.
$$H=\sum_S d_S S$$
We then shift each term by an identity.
$$H'=H+I\sum_S|d_S|$$
$$=\sum_S|d_S|(I+\sgn(d_S)S)$$
$$=\sum_S2|d_S|P_S$$
Note that $P_S$ are in fact projections since $S$ all have eigenvalues $\pm1$. Now scale $H'$:
$$H''=\frac{1}{2|d_S|}H'=\sum_S\pi_S P_S$$
Note that $H''$ is now a weighted sum of projectors. We also have $0\leq\pi_S\leq1$ and $\sum_S \pi_S=1$, so we can define the corresponding probability distribution over the choice of $S$. Now we can write the following:
$$\braket{\phi|H''|\phi}=\sum_S\pi_S\braket{\phi|P_S|\phi}=\E_S[\braket{\phi|P_S|\phi}]$$
$$\braket{\phi|P_S|\phi}=\braket{\phi|\frac{1}{2}(I+\sgn(d_S)S)|\phi}=\frac{1}{2}(1+\sgn(d_S)\braket{\phi|S|\phi})$$
Which is simple to estimate by doing the measurements corresponding to $S$.

TODO so do we have perfect completeness or no?

\subsection{Analysis and amplification}

We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
